
\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{setspace}
\onehalfspacing
\usepackage{datetime}
\usepackage{xcolor}

\begin{document}

\textbf{2} \\
\today \\
saichand avula \\
Re: Offer of Employment \\
Dear saichand avula: \\

By this letter, 2 hereby extends to you an offer of employment under the following terms and conditions.

\begin{enumerate}
    \item \textbf{Start Date.} 2025-08-01. You will be based in our office located at machavaram, sriciti, 112345.
    \item \textbf{Title.} Your title will be Cloud Engineer at 2.
    \item \textbf{Compensation.} You will be compensated on a pay 2 basis. You will be paid \$1200 per year, payable in 2's customary payroll payment procedures. You will work on a full-time basis for 2.
    \item \textbf{Fringe Benefits.} You will be entitled to 2's customary employee benefits afforded to similarly situated 2 employees.
    \item \textbf{Employment Agreement.} This agreement will be executed by 2 and you. Our goal is to work together to continue to build our business. You will report directly to 2_2. All work assignments will be given to you by 2. You will be a direct employee of 2. Your work schedule will be set by 2. Your performance reviews will be performed by 2. Only 2 has the ability to hire, fire, or discipline you for poor work performance. You will use 2 tools/instrumentalities to perform the duties of your employment. Our desire is to have a long-term relationship with you in which your compensation and role in the company are based on your performance and contribution to the company.
\end{enumerate}

Your employment relationship with 2 is at-will. You may terminate your employment with 2 at any time and for any reason whatsoever simply by notifying 2. Likewise, 2 may terminate your employment at any time and for any reason whatsoever, with or without cause or advance notice. This at-will employment relationship cannot be changed except in a writing signed by a Company officer.

We are genuinely excited about you joining 2. We look forward to a long, enjoyable, challenging, and mutually beneficial relationship with you.

\vspace{0.5in}

Sincerely, \\
[HR Signature] \\
2 \\
[HR Name] \\
[HR Title] \\

\vspace{0.5in}

\textbf{AGREED and ACCEPTED:} \\
\vspace{0.5in} \\
saichand avula \\
Date: \underline{\hspace{2in}}

\end{document}
